Fractal Patterns and Music

### 2019-12-16 paper2.tex
Update
Update paper2.tex

Mandelbrot believed in the power of the human eye to notice
“roughness”\cite{3,4}, but music provides a unique challenge, because in the
moment, music is felt in a psychological sense, and is usually not observed as a
whole, unless one acquires sheet music or other physical interpretation of the
music as the composer intended. In fact, in the memoir Benoit Mandelbrot A life
in Many Dimensions, Harlan Brothers wrote, “Benoit Mandelbrot always had a
strong feeling that music could be viewed from a fractal perspective. However,
without our eyes to guide us, how do we gain this perspective?”[ALMD] The
question posed is an excellent one, and Brothers goes on to discuss that
generally there are seven ways that fractals can appear in music.

@@

The paper Structural Scaling of Bach’s Cello Suite No.3 by Harlan Brothers is
dedicated entirely to examining the scaling characteristics within the Bourrée
Part 1 (the score of which is displayed in Figure~\ref{bach}). The structural
scaling that Brothers noticed in his Bach’s Cello Suite No. 3 can be described
by the four figures he provided below. In the section m1 and m2 of the first
figure we see two eighth notes followed by a
quarter note. This structure of Short-Short-Long is repeated throughout this
section of the piece by Bach. The section m3 is also Short-Short-Long but scaled
twice as long as the m1, and m2 section so it contains two quarter notes
followed by a section of the duration of a half note. Since m3 is twice as long
as m2 and m1, in section s1 we again see the pattern of Short-Short-Long.
Continuing in the same manner we can see how s1, s2 and s3 form a
Short-Short-Long pattern as well. In Figure~\ref{bach_scale} we can visually see
that the self-similar pattern resembles the section as a whole in three
different levels.

@@

\begin{thebibliography}{9}
\bibitem{1}
    R. F. Voss and J. Clarke,
    ``$\sfrac 1 f$ noise in music and speech'',
    Nature Vol. 258, 1975; pp. 317--318.
\bibitem{2}
    H. J. Brothers,
    ``Structural scaling in Bach's cello suite no. 3.''
    Fractals, Vol. 15, No. 1, 2007; pp. 89--95.
\bibitem{3}
    MIT Video Production.
    ``Benoit B. Mandelbrot, MIT 2001---Fractals in Science, Engineering and Finance (Roughness and Beauty)'',
        YouTube, Jan. 17, 2019 [Video file],
    accessed Dec. 10, 2019.
    \url{https://www.youtube.com/watch?v=ock9Gk_aqw4}.
\bibitem{4}
    TED.\
    ``Fractals and the art of roughness'',
    TED, Fed, 2010 [Video file],
    accessed: Dec. 10, 2019.
    \url{www.ted.com/talks/benoit_mandelbrot_fractals_and_the_art_of_roughness/discussion}.
\bibitem{5}
    H. Brothers,
    ``Fractal Music: Common Errors.''
    \url{http://www.brothers technology.com/fractal-music/errors.html}
\bibitem{6}
    H.T. David and A. Mendel,
    The Bach Reader; pp. 305--306.
\bibitem{7}
    D.R. Hofstadter,
    \emph{Godel, Escher, Bach: An Eternal Golden Braid} (Basic Books, 1980).
\bibitem{8}
    M. Bulmer,
    ``Music From Fractal Noise''
    Proceedings of the Mathematics 2000 Festival, Melbourne, Jan 13, 2000.
\bibitem{9}
    Mandelbrot, B. (1971),
    ``A Fast Fractional Gaussian Noise Generator''.
    Water Resources Research, 7; pp. 543–553.
\bibitem{10}
    Chatfield, C. (1996),
    ``The Analysis of Time Series: An Introduction'' (4th ed.).
    London: Chapman \& Hall.
\bibitem{11}
    H. Brothers,
    ``Fractal Music: Prerequisites for fractal classification'', HTML.\
    \url{http:// www.brotherstechnology.com/yale/FractalMusic/FracMusicBground/Frac}.
\bibitem{12}
    Zhi-Yuan Su and Tzuyin Wu,
    ``Multifractal analyses of music sequences'',
    Physica D 221, 2006.
\end{thebibliography}
\end{document}

>>>>

Mandelbrot believed in the power of the human eye to notice
“roughness”\cite{3,4}, but music provides a unique challenge, because in the
moment, music is felt in a psychological sense, and is usually not observed as a
whole, unless one acquires sheet music or other physical interpretation of the
music as the composer intended. In fact, in the memoir Benoit Mandelbrot A life
in Many Dimensions, Harlan Brothers wrote, “Benoit Mandelbrot always had a
strong feeling that music could be viewed from a fractal perspective. However,
without our eyes to guide us, how do we gain this perspective?”\cite{13} The
question posed is an excellent one, and Brothers goes on to discuss that
generally there are seven ways that fractals can appear in music.

@@

The paper Structural Scaling of Bach’s Cello Suite No.3 by Harlan Brothers is
dedicated entirely to examining the scaling characteristics within the Bourrée
Part 1 (the score of which is displayed in Figure~\ref{bach}). The structural
scaling that Brothers noticed in his Bach’s Cello Suite No. 3 can be described
by the four figures he provided below. In the section m1 and m2 of the first
figure we see two eighth notes followed by a
quarter note. This structure of Short-Short-Long is repeated throughout this
section of the piece by Bach. The section m3 is also Short-Short-Long but scaled
twice as long as the m1, and m2 section so it contains two quarter notes
followed by a section of the duration of a half note. Since m3 is twice as long
as m2 and m1, in section s1 we again see the pattern of Short-Short-Long.
Continuing in the same manner we can see how s1, s2 and s3 form a
Short-Short-Long pattern as well. In Figure~\ref{bach_scale} we can see again 
that the self-similar pattern resembles the section as a whole in three
different levels.

@@

\begin{thebibliography}{9}
\bibitem{1}
    R. F. Voss and J. Clarke,
    ``$\sfrac 1 f$ noise in music and speech'',
    Nature Vol. 258, 1975; pp. 317--318.
\bibitem{2}
    H. J. Brothers,
    ``Structural scaling in Bach's cello suite no. 3.''
    Fractals, Vol. 15, No. 1, 2007; pp. 89--95.
\bibitem{3}
    MIT Video Production.
    ``Benoit B. Mandelbrot, MIT 2001---Fractals in Science, Engineering and Finance (Roughness and Beauty)'',
        YouTube, Jan. 17, 2019 [Video file],
    accessed Dec. 10, 2019.
    \url{https://www.youtube.com/watch?v=ock9Gk_aqw4}.
\bibitem{4}
    TED.\
    ``Fractals and the art of roughness'',
    TED, Fed, 2010 [Video file],
    accessed: Dec. 10, 2019.
    \url{www.ted.com/talks/benoit_mandelbrot_fractals_and_the_art_of_roughness/discussion}.
\bibitem{5}
    H. Brothers,
    ``Fractal Music: Common Errors.''
    \url{http://www.brothers technology.com/fractal-music/errors.html}
\bibitem{6}
    H.T. David and A. Mendel,
    The Bach Reader; pp. 305--306.
\bibitem{7}
    D.R. Hofstadter,
    \emph{Godel, Escher, Bach: An Eternal Golden Braid} (Basic Books, 1980).
\bibitem{8}
    M. Bulmer,
    ``Music From Fractal Noise''
    Proceedings of the Mathematics 2000 Festival, Melbourne, Jan 13, 2000.
\bibitem{9}
    Mandelbrot, B. (1971),
    ``A Fast Fractional Gaussian Noise Generator''.
    Water Resources Research, 7; pp. 543–553.
\bibitem{10}
    Chatfield, C. (1996),
    ``The Analysis of Time Series: An Introduction'' (4th ed.).
    London: Chapman \& Hall.
\bibitem{11}
    H. Brothers,
    ``Fractal Music: Prerequisites for fractal classification'', HTML.\
    \url{http:// www.brotherstechnology.com/yale/FractalMusic/FracMusicBground/Frac}.
\bibitem{12}
    Zhi-Yuan Su and Tzuyin Wu,
    ``Multifractal analyses of music sequences'',
    Physica D 221, 2006.
\bibitem{13}
    Michael Frame and Nathan Cohen,
    \emph{Benoit Mandelbrot A Life in Many Dimensions} (World Scientific, 2015).
\end{thebibliography}
\end{document}
